% Autogenerated translation of about.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[12pt]{book}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,left=.5in,right=.5in,top=.3in,bottom=0.3in]{geometry}
\setlength\parindent{0pt}
\setlength{\parskip}{\baselineskip}
\renewcommand*\familydefault{\sfdefault}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}
\Large

\hrule
permalink: /
title: "Bogdan Mazoure - Math \& Stats graduate student @ McGill University"
excerpt: "About me"
author\emph{profile: true
redirect}from: 
  - /about/

\section*{  - /about.html}

\chapter*{About me}

I am currently a PhD student at the Montreal Institute for Learning Algorithms (MILA) and McGill University, co-supervised by Devon Hjelm and Doina Precup. My research interests include deep reinforcement learning, probabilistic modeling, variational inference and representation learning.

I have completed my Master's in Statistics at McGill University under the supervision of Prof. \href{http://www.math.mcgill.ca/neslehova/}{Johanna Neslehova}. My thesis focuses on reconstructing graphical models from discrete data with variational inference and multiarmed bandits. It can be found here: \href{https://bmazoure.github.io/files/thesis_Msc_2018.pdf}{link}.

I was also a research intern at Nuance during the summer of 2018 where I collaborated with Dr. \href{https://scholar.google.ca/citations?user=KRPMXqYAAAAJ&hl=en}{Atta Norouzian}. My work there focused on modeling acoustic signals such as speech with deep neural architectures.

Previously, I obtained a Bachelor's in Computer Science and Statistics in 2017 from McGill University.

\chapter*{Research interests}

\begin{itemize}
\item Deep and distributional reinforcement learning;
\item Multivariate statistics;
\item Parametric and Non-parametric Bayesian methods (Gaussian processes and variational inference);
\item Probabilistic graphical models;
\item Uncertainty representation in neural networks;
\item Generative models (auto-encoding variational Bayes and generative nets);
\item Dependence modeling for discrete marginals.
\end{itemize}

\end{document}
